### 2020-04-30 final_report/data.tex
get figure 2 sorted

Model training over high-dimensional parameter spaces may be improved in many
aspects by carefully reducing the number of variables used to describe the
space. For many applications, feature selection strategies succeed in
identifying a sufficiently representative subset of the original input
variables; however, all given variables were assumed to be physically relevant
to the MC TBR model. Feature extraction methods, on the other hand, aim to
identify a transformation of the parameter space which decreases dimensionality; even if no individual parameter is separable from the space, some linear combinations of parameters or nonlinear functions of parameters may be.

\begin{figure}[h]
	\centering
	\includegraphics[width=\linewidth]{run1_500k_tbr_vs_feat}
	\caption{Marginalised dependence of TBR on the choice of continuous
	features.}
  \label{fig:tbr-vs-features}
\end{figure}

% TODO: tie the figure above to the paragraph above

>>>>

Model training over high-dimensional parameter spaces (illustrated
in~\cref{fig:tbr-vs-features}) may be improved in many
aspects by carefully reducing the number of variables used to describe the
space. For many applications, feature selection strategies succeed in
identifying a sufficiently representative subset of the original input
variables; however, all given variables were assumed to be physically relevant
to the MC TBR model. Feature extraction methods, on the other hand, aim to
identify a transformation of the parameter space which decreases dimensionality; even if no individual parameter is separable from the space, some linear combinations of parameters or nonlinear functions of parameters may be.

\begin{figure}[h]
	\centering
	\includegraphics[width=\linewidth]{run1_500k_tbr_vs_feat}
	\caption{Marginalised dependence of TBR on the choice of continuous
	features in \num{500000}~points collected in run~1. Points are coloured by density.}
  \label{fig:tbr-vs-features}
\end{figure}
